%% Minimal standalone to render the AION-1 title/abstract box.
%% Build from this directory: lualatex titlepage-standalone.tex
\documentclass[]{polymathic}
\usepackage{amssymb}
\usepackage[sort&compress]{natbib}
\usepackage{aas_macros}

\title{AION-1: Omnimodal Foundation Model for Astronomical Sciences}

\author[*,1,2,3,4]{Liam Parker}
\author[*,5,2]{Francois Lanusse}
\author[*,6]{Jeff Shen}
\author[7]{Ollie Liu}
\author[8]{Tom Hehir}
\author[3]{Leopoldo Sarra}
\author[3]{Lucas Meyer}
\author[9]{Micah Bowles}
\author[2,3]{Sebastian Wagner-Carena}
\author[2]{Helen Qu}
\author[2,3]{Siavash Golkar}
\author[2]{Alberto Bietti}
\author[10]{Hatim Bourfoune}
\author[10]{Nathan Cassereau}
\author[10]{Pierre Cornette}
\author[2,11]{Keiya Hirashima}
\author[2]{Geraud Krawezik}
\author[2]{Ruben Ohana}
\author[3]{Nicholas Lourie}
\author[2,3]{Michael McCabe}
\author[2]{Rudy Morel}
\author[1,8]{Payel Mukhopadhyay}
\author[12]{Mariel Pettee}
\author[2]{Bruno Regaldo-Saint Blancard}
\author[3]{Kyunghyun Cho}
\author[8]{Miles Cranmer}
\author[2,3,6]{Shirley Ho}

\affiliation[1]{University of California, Berkeley}
\affiliation[2]{Flatiron Institute}
\affiliation[3]{New York University}
\affiliation[4]{Lawrence Berkeley National Laboratory}
\affiliation[5]{Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM}
\affiliation[6]{Princeton University}
\affiliation[7]{University of Southern California}
\affiliation[8]{University of Cambridge}
\affiliation[9]{University of Oxford}
\affiliation[10]{IDRIS, CNRS}
\affiliation[11]{RIKEN Center for iTHEMS}
\affiliation[12]{University of Wisconsin--Madison}

\contribution[*]{Equal Contribution.}

\abstract{While foundation models have shown promise across a variety of
fields, astronomy still lacks a unified framework for joint modeling across its
highly diverse data modalities. In this paper, we present AION-1, a family of
large-scale multimodal foundation models for astronomy. AION-1 integrates
heterogeneous imaging, spectroscopic, and scalar data using a two-stage
architecture: modality-specific tokenization followed by transformer-based
masked modeling of cross-modal token sequences. The model is pretrained on five
large-scale surveys: Legacy Survey, Hyper Suprime-Cam (HSC), Sloan Digital Sky
Survey (SDSS), Dark Energy Spectroscopic Instrument (DESI), and Gaia. These
span more than 200 million observations of stars, galaxies, and quasars. With a
single frozen encoder, AION-1 achieves strong results on a broad suite of
downstream tasks, including galaxy and stellar property estimation, galaxy
morphology classification, similarity-based retrieval, galaxy image
segmentation, and spectral super-resolution. We release AION-1 model variants
ranging from 300 M to 3.1 B parameters. Beyond astronomy, AION-1 provides a
scalable blueprint for multimodal scientific foundation models that can
seamlessly integrate noisy, instrument-specific observations. All code,
tokenizers, pretrained weights, and a lightweight evaluation suite are released
under an open-source license.}

\date{October 2025}
\titlecorrespondence{Liam Parker: \texttt{lhparker@berkeley.edu}; Francois Lanusse: \texttt{francois.lanusse@cnrs.fr}}
\titlecode{\url{https://github.com/PolymathicAI/AION/}}

\begin{document}
\maketitle
\end{document}
